Active Learning : From Blackbox To Timed Connectors

### 2015-12-28 paper/paper.tex
.

\usepackage{amssymb}
\usepackage{cite}
\usepackage[normalem]{ulem}
% FIXME finally no todos should exist in this draft
\usepackage[textsize=tiny]{todonotes}
% positioning is used for below lef = of
\usetikzlibrary{shapes,arrows,automata,positioning}
% some tikz-styles on reo channels, not required in papers that have nothing to do with Reo

@@

@@

\subsection{Parameterized Mealy Machine}
\begin{definition}[Parameterized Mealy Machine]
  A \emph{Parameterized Mealy Machine} is defined as a function $\mathcal{PM}(\Sigma)=\langle
  S(\Sigma), s_0, I(\Sigma), O(\Sigma), \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an
  alphabet to its corresponding Mealy Machine. 
  \begin{itemize}
    \item[-] $\Sigma$ is a \emph{finite} datum alphabet (hereafter referred to as an alphabet)
    \item[-] $S$ is a function that maps an alphabet to a \emph{finite} set of
      states. We use $S(\Sigma)$ to denote the state set.
    \item[-] $I(\Sigma)$ maps an alphabet to a set of input actions.
    \item[-] $O(\Sigma)$ maps an alphabet to a set of output actions.
    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
    \item[-] $\delta$ maps a \emph{finite} datum alphabet to an \emph{output function}. We use
      $\delta(\Sigma):S(\Sigma)\times I(\Sigma)\rightarrow O(\Sigma)$ to denote the output function.
    \item[-] $\lambda$ maps an alphabet to a \emph{transition function}. We use
      $\lambda(\Sigma):S(\Sigma)\times I(\Sigma)\rightarrow S(\Sigma)$ to denote the transiton
      function.
  \end{itemize}
\end{definition}

Now we can use Parameterized Mealy Machines to define a new semantics to Reo.
\begin{example}[PMM Semantics of FIFO channel $PM_{FIFO}$]
  The semantics of FIFO channel with source end $A$ and sink end $B$ can be defined as follows
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
    \item[-] $I(\Sigma)=\{(A:d)|d\in\Sigma\cup \{\bot\}\}$
    \item[-] $O(\Sigma)=\{(B:d)|d\in\Sigma\cup\{\bot\}\}$
    \item[-] transition function
      \begin{displaymath}
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[h]{ll}
          q_d & s=q_0\land i=(A:d) \\
          q_d & s=q_{d'}\land i=(A:d) \\
          q_0 & s=q_d\land i=(A:\bot) \\
        \end{array}
        \right.
      \end{displaymath}
    \item[-] output function
      \begin{displaymath}
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[h]{ll}
          q_d & s=q_0\land i=(A:d) \\
          q_d & s=q_{d'}\land i=(A:d) \\
          q_0 & s=q_d\land i=(A:\bot) \\
        \end{array}
        \right.
      \end{displaymath}
  \end{itemize}
\end{example}

@@

\todo{finish the definition ..}
\begin{definition}[Production of Parameterized Mealy Machines]
  Now we're going to define the production of two parameterized mealy Machine
  \[
  Prod(PM_1,PM_2)=PM_3
  \]
  as follows,
  \begin{itemize}
    \item[-] $\forall\Sigma,PM_3.I(\Sigma)=PM_1.I(\Sigma)\cup PM_2.I(\Sigma)$
    \item
  \end{itemize}
\end{definition}

@@

\section{Case Studies}

>>>>

\usepackage{amssymb}
\usepackage{cite}
\usepackage[normalem]{ulem}
% for a smile-face character
\usepackage{wasysym}
% FIXME finally no todos should exist in this draft
\usepackage[textsize=tiny]{todonotes}
% positioning is used for below lef = of
\usetikzlibrary{shapes,arrows,automata,positioning}
% some tikz-styles on reo channels, not required in papers that have nothing to do with Reo

@@

% personal characters
\newcommand{\rblock}[0]{\circleddash}
\newcommand{\rread}[0]{\smiley}
\newcommand{\rnoread}[0]{\frownie}

@@

\subsection{Parameterized Mealy Machine}
\begin{definition}[Parameterized Mealy Machine]
  A \emph{Parameterized Mealy Machine} is defined as a function $\mathcal{PM}(\Sigma)=\langle
  S(\Sigma), s_0, I, O, \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an
  alphabet to its corresponding Mealy Machine. 
  \begin{itemize}
    \item[-] $\Sigma$ is a \emph{finite} datum alphabet (hereafter referred to as an alphabet)
    \item[-] $S$ is a function that maps an alphabet to a \emph{finite} set of
      states. We use $S(\Sigma)$ to denote the state set.
    \item[-] $I$ is a finite set of source-ends.
    \item[-] $O$ is a finite set of sink-ends.
    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
    \item[-] $\delta$ maps a \emph{finite} datum alphabet to an \emph{output function}. We use
      $\delta(\Sigma):S(\Sigma)\times Input(\Sigma,I)\rightarrow Output(\Sigma, O)$ to denote the output function.
    \item[-] $\lambda$ maps an alphabet to a \emph{transition function}. We use
      $\lambda(\Sigma):S(\Sigma)\times Input(\Sigma,I)\rightarrow S(\Sigma)$ to denote the transiton
      function.
  \end{itemize}
\end{definition}

In the definition above, \emph{Input} and \emph{Output} are used to generate input actions and output actions by the corresponding alphabets and ends.
\todo{How to say?}
\[
Input(\Sigma,I)=\{\}
\]
\[
Output(\Sigma,I)=\{\}
\]

Now we can use Parameterized Mealy Machines to define a new semantics to Reo.
\begin{example}[PMM Semantics of FIFO channel $PM_{FIFO}$]
  The semantics of FIFO channel with source end $A$ and sink end $B$ can be defined as follows
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
    \item[-] $I=\{A\}$
    \item[-] $O=\{B\}$
    \item[-] $s_0=q_0$
    \item[-] output function
      \begin{displaymath}
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[h]{ll}
          (B:\bot) & s=q_0\land i=(A:\_,B:\rnoread) \\
          (B:d) & s=q_0\land i=(A:d,B:\rread)\\
          \rblock & s=q_0\land i=(A:\bot,B:\rread) \\
          (B:d) & s=q_d\land i=(A:\_,B:\rread)\\
          \rblock & s=q_d\land i=(A:d,B:\rnoread) \\
          (B:\bot) & s=q_d\land i=(A:\_,B:\rnoread) \\     
        \end{array}
        \right.
      \end{displaymath}
    \item[-] transition function
      \begin{displaymath}
        \lambda(\Sigma)(s,i)=\left\{
        \begin{array}[h]{ll}
          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
          q_0 & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
  \end{itemize}
\end{example}

@@

\todo{finish the definition ..}
\begin{definition}[Production of Parameterized Mealy Machines]
  Now we're going to define the production operator \emph{prod} of two parameterized mealy machines as,
  \[
  prod(PM_1,PM_2)=PM_3
  \]
  as follows, 
  \begin{itemize}
  	\item[-] $\forall\Sigma, PM_3.S(\Sigma)=PM_1.S(\Sigma)\times PM_2.S(\Sigma)$
    \item[-] $PM_3.I=PM_1.I\cup PM_2.I-PM_1.O\cup PM_2.O$
    \item[-] $PM_3.O=PM_1.O\cup PM_2.O-PM_1.I\cup PM_2.I$
    \item[-] $PM_3.s_0=(PM_1.s_0, PM_2.s_0)$
    \item[-] $\forall\Sigma, PM_3.\delta(\Sigma)((s_1,s_2), i)=$
      \begin{displaymath}
        \left\{
        \begin{array}[h]{ll}
          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
          q_0 & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
    \item[-] $\forall\Sigma, PM_3.\lambda(\Sigma)((s_1,s_2),i)=$
      \begin{displaymath}
        \left\{
        \begin{array}[h]{ll}
          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
          q_0 & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
  \end{itemize}
\end{definition}

@@

\section{Case Studies}
\subsection{Alternator}
\subsection{Timed TODO}
